---
title: "Bibliography"
author: "hmeasure.net"
date: "5 February 2017"
output: html_document
bibliography: hmeasure.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

The package is available on [](CRAN) so all you need to do is: 

```{r, echo=TRUE, eval=FALSE}
install.packages('hmeasure')
library(hmeasure)
```

```{r, echo=FALSE}
library(hmeasure)
```
## Documentation
The package is extensively documented, and also has a detailed vignette outlining not only usage but also enough theory / terminology around classification performance:

```{r, echo=TRUE, eval=FALSE}
help(HMeasure)
vignette('hmeasure')
```

## Example 

The example below assumes you understand the basics of classification performance. If not, your best starting point is the package [https://cran.r-project.org/web/packages/hmeasure/vignettes/hmeasure.pdf](vignette). 

We start by loading the classifier:

```{r}
# load the data
library(MASS) 
library(class) 
data(Pima.te) 

# split it into training and test
pima.train <- Pima.te[seq(1,dim(Pima.te)[1],3),]
pima.test <- Pima.te[-seq(1,dim(Pima.te)[1],3),]
true.class<-pima.test[,8]

# train an LDA classifier
pima.lda <- lda(formula=type~., data=pima.train)
out.lda <- predict(pima.lda,newdata=pima.test) 

# obtain the predicted labels and classification scores
scores.lda <- out.lda$posterior[,2]

# train k-NN classifier
class.knn <- knn(train=pima.train[,-8], test=pima.test[,-8],
  cl=pima.train$type, k=9, prob=TRUE, use.all=TRUE)
scores.knn <- attr(class.knn,"prob")
# this is necessary because k-NN by default outputs
# the posterior probability of the winning class
scores.knn[class.knn=="No"] <- 1-scores.knn[class.knn=="No"] 

# run the HMeasure function on the data frame of scores
scores <- data.frame(LDA=scores.lda,kNN=scores.knn)
results <- HMeasure(true.class,scores)

# report aggregate metrics
summary(results,show.all=TRUE)

# produce the four different types of available plots
par(mfrow=c(2,2))
plotROC(results,which=1)
plotROC(results,which=2)
plotROC(results,which=3)
plotROC(results,which=4)
```